---
title: "Weight of Fish"
author: "leia"
date: "`fall2023`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse) 
library(dplyr) 
library(leaps) 
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight

Find the best model using two variables to predict perch weight, and compare this to the best overall model. 

## Perch

```{r}
perch = filter(fish, Species == "Perch")
```

### Best Two regressor model

```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = perch)
summary(modelPerch)
```


```{r}
best2Perch = lm(Weight ~ Height + Width, data = perch)
summary(best2Perch)
```
## best 2-variable equation
Weight = -536 + 74.77*Height + 69.62*Width 


## Pike
```{r}
pike = filter(fish, Species == "Pike")
```


### Best Two regressor model
```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = pike) 
summary(modelPike)
```

```{r}
best2Pike = lm(Weight ~ Length1 + Length3, data = pike)
summary(best2Pike)
```

## Best 2-variable equation

weight = -1675.79 + -105.64*Length1 + 141.25*Length3 

## Roach
```{r}
Roach = filter(fish, Species == "Roach")
```

### Best Two regressor model
```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Roach) 
summary(modelRoach)
```
```{r}
best2Roach = lm(Weight ~ Length1 + Length3, data = pike)
summary(best2Roach)
```
## Best 2-variable equation

## Final Summary Statements 

